A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-19 latex/main.tex
Tweak the ACKs

SHZ acknowledges support from
Oxford Population Health, University of Oxford
(NDPH Intermediate Research Fellowship)
and
% Apparently, it is now Johnson & Johnson Innovative Medicine.
Janssen Pharmaceuticals
(Oxford-Janssen Translational Genomics Fellowship).
IG is supported by Wellcome (DPhil in Genomic Medicine and Statistics, 228319/Z/23/Z).
DSP acknowledges funding administered by the Danish National Research Foundation
in support of the Pioneer Centre for SMARTbiomed.
% "acknowledges support" here means "was awarded this grant 
% and it supported this research"
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from R01 HG012473 from the National Institutes of Health NHGRI, EPSRC (research grant EP/X024881/1) and the Robertson Foundation. For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.

>>>>

SHZ is supported by an NDPH Intermediate Research Fellowship (Oxford Population
Health, University of Oxford).
IG is supported by Wellcome (DPhil in Genomic Medicine and Statistics, 228319/Z/23/Z).
DSP acknowledges funding administered by the Danish National Research Foundation
in support of the Pioneer Centre for SMARTbiomed.
SO acknowledges support from the Natural Sciences and Engineering Research Council of Canada (RGPIN-2022-03726).
JK acknowledges support from the
Oxford-Janssen Translational Genomics Fellowship,
research grant R01 HG012473 from the National Institutes of Health NHGRI, 
research grant EP/X024881/1 from the Engineering and Physical Sciences Research Council, 
and the Robertson Foundation. 
For the purpose of Open Access, the authors have applied a CC BY public copyright licence to any Author Accepted Manuscript version arising from this submission.
